Figure 3. Tissue Microbiome Abundances

### 2022-02-02 reports/rmarkdown/manuscript/Figure3.Rmd
Remove white space from figure

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Figure 3., echo=FALSE, warning=FALSE, message=FALSE, fig.width=6 ,fig.asp=1, fig.pos="t"}
### A + B
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters

layout(matrix(c(1,1,1,1,1,1,
                2,2,2,2,2,2,
                3,3,6,7,4,4,
                3,3,6,5,4,4,
                8,8,8,8,8,8) , ncol= 6,byrow = T),
                               widths = c(1.2,1,1.83,1.7,.85,1.4),
                               heights = c(.7,1.5,.8,1.5,1,.8,.2))

@@

### C
############################
# TOTAL RELATIVE ABUNDANCE #
############################
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
sample_use <- colnames(TRX)[colSums(TRX)!=0]
raw <- c("ASV_CVL_V3", "ASV_tissue_V3") %>% set_names()
raw_list <- raw %>%
  map(., ~read_csv(paste0("../../../results/",.x,"_raw_counts.csv")))  %>%
  map(., ~column_to_rownames(., var = "X1")) %>%          
  map(., ~dplyr::select(., any_of(sample_use)))

@@

par(mar=c(6,5,2,.3)) #b,l,t,r
barplot( r, border = NA ,ylab="abundance", xlab ="", axisnames = F,
         col = taxa_pal[factor(rownames(r),levels = lvl)])
title(main = "Total relative abundance ", line = 0.5, cex.main = .9, font.main= 1)
mtext("Luminal        Tissue ", line = 0, cex=.6, side=1)

@@

### D
#############################
# LUMINAL-TISSUE COMPARISON #
#############################
par(mar=c(5,1.1,2,2)) #b,l,t,r
x <- as.character(metadata[,"Luminal_gr"])
x[is.na(x)] <- "NA"
y <- as.character(metadata[,"Tissue_gr"])
y[is.na(y)] <- "NA"
x1 <- x [ (x!="NA") & (y!="NA") ]
y1 <- y [ (x!="NA") & (y!="NA") ]
df <- data.frame(x1,y1)
plot_sankey( df,color_by = 1, 
             plot_labels = T, plot_weights = F,order_1_by = "NULL",
             order_2_by = "disentangled",use_w1 = T,use_w2 = T,gap2v = 0,smoothing = .1,
             pal= pal)
text(c(0,1),c(1,1),labels = c( "Luminal" , "Tissue" ),pos=3, xpd=T)

@@

par(mar=c(0,.2,1,.4)) #b,l,t,r
empty_plot()
legend(x = par("usr")[c(1)],
         y = par("usr")[c(4)],
         legend = lvl[1:12],xjust = 0,yjust = 1,
         bty = "n",pch = 22,pt.cex = 2,cex = 1,xpd=T,
         pt.bg = taxa_pal)

par(mar=c(0,0,1,1)) #b,l,t,r
empty_plot()
legend(x = par("usr")[c(1)],
         y = par("usr")[c(4)],
         legend = lvl[13:17],xjust = 0,yjust = 1,
         bty = "n",pch = 22,pt.cex = 2,cex = 1,xpd=T,
         pt.bg = taxa_pal[13:17])

empty_plot()
```

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Figure 3., echo=FALSE, warning=FALSE, message=FALSE,  fig.pos="t"}
#  fig.width=6 ,fig.asp=1, fig.height=7,
### A
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters

layout(matrix(c(1,1,1,1,1,1,
                2,2,2,2,2,2,
                3,3,6,7,4,4,
                3,3,6,5,4,4) , ncol= 6,byrow = T),
                               widths = c(1.2,1,1.83,1.7,.85,1.4),
                               heights = c(.7,1.6,1,1.1,1,.8,.2))

@@

### B
############################
# TOTAL RELATIVE ABUNDANCE #
############################
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
sample_use <- colnames(TRX)[colSums(TRX)!=0]
raw <- c("ASV_CVL_V3", "ASV_tissue_V3") %>% set_names()
raw_list <- raw %>%
  map(., ~read_csv(paste0("../../../results/",.x,"_raw_counts.csv")))  %>%
  map(., ~column_to_rownames(., var = "X1")) %>%          
  map(., ~dplyr::select(., any_of(sample_use)))

@@

par(mar=c(1.5,5,2,.3)) #b,l,t,r
barplot( r, border = NA ,ylab="abundance", xlab ="", axisnames = F,
         col = taxa_pal[factor(rownames(r),levels = lvl)])
title(main = "Total relative abundance ", line = 0.5, cex.main = .9, font.main= 1)
mtext("Luminal        Tissue ", line = 0, cex=.6, side=1)

@@

### C
#############################
# LUMINAL-TISSUE COMPARISON #
#############################
par(mar=c(0,1.1,2,2)) #b,l,t,r
x <- as.character(metadata[,"Luminal_gr"])
x[is.na(x)] <- "NA"
y <- as.character(metadata[,"Tissue_gr"])
y[is.na(y)] <- "NA"
x1 <- x [ (x!="NA") & (y!="NA") ]
y1 <- y [ (x!="NA") & (y!="NA") ]
df <- data.frame(x1,y1)
plot_sankey( df,color_by = 1, 
             plot_labels = T, plot_weights = F,order_1_by = "NULL",
             order_2_by = "disentangled",use_w1 = T,use_w2 = T,gap2v = 0,smoothing = .1,
             pal= pal)
text(c(0,1),c(1,1),labels = c( "Luminal" , "Tissue" ),pos=3, xpd=T)

@@

par(mar=c(0,.2,1.5,.4)) #b,l,t,r
empty_plot()
legend(x = par("usr")[c(1)],
         y = par("usr")[c(4)],
         legend = lvl[1:12],xjust = 0,yjust = 1,
         bty = "n",pch = 22,pt.cex = 2,cex = 1,xpd=T,
         pt.bg = taxa_pal)

par(mar=c(0,0,1.5,1)) #b,l,t,r
empty_plot()
legend(x = par("usr")[c(1)],
         y = par("usr")[c(4)],
         legend = lvl[13:17],xjust = 0,yjust = 1,
         bty = "n",pch = 22,pt.cex = 2,cex = 1,xpd=T,
         pt.bg = taxa_pal[13:17])
